Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-05-01 paper/ms.tex
update ms

\begin{figure*}[!t]
  \begin{center}
    \leavevmode
    \includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
  \end{center}
  \vspace{-0.6cm}
  \caption{
    {\bf Kepler's demographic cliff,} visible in the
    rotation-derived ages of stars (left) and planet hosts
    (right) in the Kepler field.
    The 
    light gray histograms correspond to all
    \nuniqstarsantosrotteffcut\
    $T_{\rm eff}\in[3800,6200]\,$K Kepler stars with reported
    rotation periods, and all 
    \nplhoststarwgyroage\ planet-hosting stars with reported
    rotation periods.
    The black histograms impose necessary quality cuts
    on factors such as
    binarity, crowding, and the star's evolutionary state
    (Section~\ref{subsec:flags}).
    In detail, these ``histograms'' are resampled from the posterior
    probability distributions.
    {\bf todo: numbers dont match.  why?}
    \label{fig:hist_tgyro}
  }
\end{figure*}

>>>>

\begin{figure*}[!t]
  \begin{center}
    \leavevmode
    \includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240430_maxage3200.pdf}
  \end{center}
  \vspace{-0.6cm}
  \caption{
    {\bf Kepler's demographic cliff,} visible in the rotation-derived
    ages of stars (left) and planet hosts (right) in the Kepler field.
    The lightly colored histograms correspond to all
    \nuniqstarsantosrotteffcut\ $T_{\rm eff}\in[3800,6200]\,$K Kepler
    stars with reported rotation periods, and all
    \nplhoststarwgyroage\ planet-hosting stars with reported rotation
    periods.
    The darker histograms impose necessary quality cuts on factors
    such as binarity, crowding, and the star's evolutionary state
    (Section~\ref{subsec:flags}).
    In detail, these ``histograms'' are resampled from the posterior
    probability distributions.
    Completeness is near unity until $\approx$3\,Gyr
    \citep{2022ApJ...937...94M}.
    {\bf todo: numbers dont match.  why?}
    \label{fig:hist_tgyro}
  }
\end{figure*}
